{\fontfamily{ptm}\selectfont An Inexact Accelerated Proximal Gradient Method for Large Scale Robust TV Variation Problems}

### 2025-09-07 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
TwT, fixes

\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for Large Scale Robust TV Variation Problems}}

@@

                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}y_k: D_f(x, \tilde x) \le (1/2)\Vert x - \tilde x\Vert^2, 

@@

    Our proposed algorithm allows inexact evaluation of $\hprox_{B^{-1}g\circ D}$. 
    This proximal operator can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it will bypass the need of any matrix inversion involving $D$. 

@@

        \argmin_{y, z} \left\lbrace
            g(y) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 : Az = y, y\in \RR^{m_2}, z\in \RR^{n}

@@

    Solving this problem inexactly is not difficult. 
    First order method such as Chambolle Pock will suffice, and it won't need expensive matrix inversion. 
    And, taking the gradient of $\nabla f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 

>>>>

\title{{\fontfamily{ptm}\selectfont An Inexact Accelerated Proximal Gradient Method for Large Scale Robust TV Variation Problems}}

@@

                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}(y_k): D_f(x_k, y_k) \le (B_k/2)\Vert x_k -  y_k\Vert^2, 

@@

    Our proposed algorithm allows inexact evaluation of the proximal operator of $g\circ D$. 
    It can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it can bypass the need of any matrix inversion involving $D$. 

@@

        \argmin_{z} \left\lbrace
            g(Dz) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2

@@

    First order method such as Chambolle Pock can optimize the problem inexactly without matrix inversion. 
    And, taking the gradient of $f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 
